\section{Background}\label{sec:background}

\begin{itemize}
\item General introduction: Cellular and local networks, \ac{IoT}, \ac{M2M}, \ac{D2D}. Why Cooperation?
\item Specific introduction: Data multicasting, tools for simulation of network coding, Multihop for data dissemination.
\item Specific problems to that should be addressed by the thesis: (i) Ideal codes for data dissemination to a large cluster of devices in a centralized manner, (ii) software tools for network coding simulations, (iii) Decentralized cooperation for spatial redudancy to enhance connectivities in multihop networks with Kodo + ns-3.
\item Introduction on network coding, RLNC and how does it help to the previous.
\end{itemize}

The exponential tendency for data demand predicted by major network providers \cite{cisco2016forecast} is evident. The use of data networks have become a topic of widespread audiences. The reason has been the flourishement of online applications services from the past decade to this date such as:  Whatsapp, Viber (voice and messaging), Facebook, Twitter, Snapchat, Instagram, Google+ (social networking), YouTube, Netflix, SoundCloud, Spotify (video or audio streaming), Google Drive, Dropbox and OneDrive (data storage). Also, these applications have been developed not only for a desktop \ac{PC} but also mobile smartphones and/or tablets that support either the Android, iOS or Windows Mobile \ac{OS}. Hence, the data growth is and will continue being due to mobile users.

From all these services, streaming applications that are based in scenarios where a transmitter needs to serve tens, hundreds or even thousands of receivers are becoming more frequent. These types of scenarios pose tight requirements in terms of data throughput and delay to ensure a satisfactoring \ac{QoE}. Also, from the mobile users perspective, energy consumption due to data transmissions has become a limiting factor in terms of battery life. The reason is that mobile devices perform much more internal tasks than older devices 10 years ago. Therefore, mobile network designers need to consider mechanisms and techniques that aim for high throughput and low energy consumption.

Besides the large acceptance from mobile users, another major use case for data demand will be the \ac{IoT} where millions of data collecting devices such as sensors or small actuators will be widespread deployed in homes, businesses and green common areas to provide the automation of many services. These type of services may or may not use cellular networks and might be deployed in a decentralized an unplanned manner.  

% Network Coding
Introduced by Alshwede et al. \cite{ahlswede2000network}, \ac{NC} appeared as an effective technology to remove the limitations presented previously. In this work, the authors presented a new paradigm for conveying information in communication networks. Instead of following the convention of forwarding data packets from two different data flows, the packets are mixed to create new coded packets. To decode, by receiving a coded packet and knowing the original packets, it is possible to extract the missing information. This key idea let the research community know for the first time that it was possible to code on a \textit{network} basis and not only on a \textit{link} basis as conventional \ac{FEC} technologies do.

% RLNC and applications