% mainfile: ../master.tex
\chapter*{Acknowledgments\markboth{Acknowledgments}{Acknowledgments}}\label{ch:acknowledgments}
\pagestyle{fancy}
\addcontentsline{toc}{chapter}{Acknowledgments}

All the experiences during the path of the PhD for the last three years have been incredible, very enriching and very enlightening both at a personal and technical level. These lines express my gratitude to all the people in this process.

I want to first thank my supervisors for taking out the best of me during these years and believe in me. I knew from the first day and will always remember that guiding a person is a much valuable task. To my main supervisor, Dr. Daniel Lucani, for making my work strong, having time for my questions and making me think critically and look at the correct problems. To my co-supervisor, Dr. Janus Heide, for giving me a structured approach to problem solving, the everyday tasks and guiding me in the Crossfire Project. To my co-supervisor, Dr. Frank Fitzek, for giving me good advices on how to innovate, conduct my work and be there when required. I also want to thank Dr. Muriel M\'edard for being interested in my work to present it at MIT.

None of this would have been possible without the help of my family. I want to thank in a reciprocal manner my wife Olga for her love, her patience and for being my partner in this journey. She always provided me the support in all my experiences of the PhD. To my family, who always encourage me to achieve my goals and giving me the core values and support that guided me these years: persistance, diligence and kindness.

From my everyday life at work, I have to give special thanks to my peers at Steinwurf, Chocolate Cloud, Aalborg University, both the lab and the APNet and WCN sections specially the administrative staff for helping me to handle the thesis and the Crossfire Project for providing technical experience and a world class research network. From my life in Denmark, to all my friends and acquaitances that remind me that we only have one life to live. These lists are so long that I will need several pages. So to all of you, my deepest thanks!

Finally, some people think that doing a PhD is finding all the answers, when is actually asking critical questions both technical and even personal. Therefore, I want to share with \textit{you} two quotes that summarize my personal feelings of the PhD, since they represent what I think are the purpose of research and the persons that join us in the path of life.

\vfill
\hfill V.V.V.V.V. - \textbf{V}i \textbf{v}eri \textbf{v}niversum \textbf{v}ivus \textbf{v}ici:

\hfill \textit{``By the power of truth, I, while living, have conquered the universe''}

\hfill ---'V' from V for Vendetta quoting the Faust

\hfill \textit{``Go alone and you will go fast, go together and you will get far''}

\hfill ---Ancient Proverb (Variant)


\vfill
\hfill N\'estor J. Hern\'andez Marcano

\hfill Aalborg University, \today