% mainfile: ../master.tex
\chapter*{Preface\markboth{Preface}{Preface}}\label{ch:preface}
\pagestyle{fancy}
\addcontentsline{toc}{chapter}{Preface}

This PhD thesis presents a collection of papers which consist on the research
topics that were investigated throughout the three years of my
PhD studies. The first half was as a member of the Antennas, Propagation
and Radio Networking Group (APNet), Department of Electronic Systems, Aalborg
University. The second half was as a member of the Wireless Communication
Networks (WCN) section of the same department.


This thesis was prepared under the main supervision of Assoc. Prof.
Daniel E. Lucani of the WCN section, Deparment of Electronic Systems at
Aalborg University and co-supervisions of Dr. Janus Heide, CEO of Steinwurf
ApS, Denmark; and Professor Frank H.P.
Fitzek of the Technische Universit\"{a}t of Dresden, Germany. This work was
mainly financed by the EU FP7 Marie Curie Initial Training Network CROSSFIRE
(unCooRdinated netwOrk StrategieS for enhanced interFerence, mobIlity, radio
Resource, and Energy saving management in LTE-Advanced networks) Project
from the European Commission FP7 Framework (Grant No. EU - FP7 - CROSSFIRE -
317126).


It was also partially financed by the Green Mobile Cloud project
granted by the Danish Council for Independent Research (Grant No. DFF -
0602-01372B). The thesis includes four selected publications as its
fundamental body and a complete list of all co-authored publications.

\vfill
\hfill N\'estor J. Hern\'andez Marcano

\hfill Aalborg University, \today
